Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-04-30 cikm2016/futurework.tex
Some more text trimming.

In this paper, we have only considered the parsing of strings, but dates are often formatted as integers (\eg \texttt{201507016}). It is significantly faster to decompose integers into date parts using arithmetic operations (\eg \texttt{mod} and \texttt{div}) than by using slower, locale-sensitive string parsing functions. Moreover, the number of possible formats is low enough that we may be able to enumerate them. Timestamp preparation from numeric representations is another form of preparation which we would like to automate.

>>>>

In this paper, we have considered the parsing of strings, but dates are often formatted as integers (\eg \texttt{201507016}). It is significantly faster to decompose integers into date parts using arithmetic operations (\eg \texttt{mod} and \texttt{div}) than by using locale-sensitive string parsing functions. Timestamp preparation from numeric representations is another form of preparation which we would like to automate.

### 2016-04-30 cikm2016/testing.tex
Some more text trimming.

Similar to the MDL algorithm described in the previous subsection, the CYK parser is run over the same set of samples from each validation file to generate a ranked list of parse trees representing the date-time formats. As a second pass of the parser, starting from the most probable parse tree, each parse tree is then applied to the entire file's columnar data to determine the dominant pattern(s). For the second pass, we can parallelize the CYK parsing because the dependencies between reapplying the ranked list of parse trees are very sparse.

>>>>

Similar to the MDL algorithm, the CYK parser is run over the same set of samples from each validation file to generate a ranked list of parse trees representing the date-time formats. As a second pass of the parser, starting from the most probable parse tree, each parse tree is then applied to the entire file's columnar data to determine the dominant pattern(s). For the second pass, we can parallelize the CYK parsing because the dependencies between reapplying the ranked list of parse trees are very sparse.
